Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-10 paper/ms.tex
more acks

\acknowledgments
It is a pleasure to thank
Sivaram Ambikasaran,
Will Farr,
and
David W.\ Hogg
for helpful contributions to the ideas and code presented here.

>>>>

\acknowledgments
It is a pleasure to thank
Sivaram Ambikasaran,
Megan Bedell,
Will Farr,
Sam Grunblatt,
David W.\ Hogg, and
Dan Huber
for helpful contributions to the ideas and code presented here.
